---
title       : Predicting exercise types. As easy as apple pie.
subtitle    : 
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

```{r echo=FALSE}
library(caret);
library(rpart);
library(randomForest);

set.seed(42);

load("modelObjectState.rda");

trainData <- read.csv("pml-training.csv", na.strings=c("NA","#DIV/0!", ""));
trainData <- trainData[,colSums(is.na(trainData)) == 0];


irreleventIdxs <- grep("(*timestamp*)|(user_name)|(*_window)|(X)", names(trainData));
trainData   <- trainData[, -irreleventIdxs];
trainIdxs <- createDataPartition(y=trainData$classe, p=0.75, list=FALSE);
subTest   <- trainData[-trainIdxs, ];
```

```{r}
p2 <- predict(modelObject, subTest, type = "class");
accuracy <- sum(p2 == subTest$classe)/length(p2);
oosError <- 1 - accuracy;
oosErrorPercentage <- paste0(round(oosError * 100, digits = 2), "%");
print(paste0("oosPercentage: ", oosErrorPercentage));
```

## Problem

We did great prediction model as part of 'Practical machine learning course': out of Sample error is `r oosErrorPercentage` only. But it is too ascetic, and is not intended for wide audience.

--- .class #id 

## Solution

Let's convert it to web-app, so everybody can use it.

--- .class #id 


## Development problems

-We can't just copy all the core logic into server.R since model training takes a lot of time. 

-Train files are huge. 

Let's just pretrain model. This will decrease server responce time dramatically, and decrease application size.
Note: test data is required still

--- .class #id 


## Conclusion

Try our ACME application today. 

The one and only AI-capable application to predict exercice type with Out-Of-Sample error as low as `r oosError`, for free. Knowledge of the ancients within your browser. 

Unbelievable!

